Hardware-in-the-Loop Plant Modeling for Autonomous Vehicle

### 2022-03-21 reportTII-ArticleHIL.tex
Worked on the structure of the final report

The example given in~\cite{example1} shows how to create an iddata object from a
dataset in order to get the inputs and the outputs. The next step was to look at
the impulse and step responses in order to learn more about how the inputs and
outputs act. From there the state space model was estimated using the first part
of the given data. This model was compared to the step responses and with the
second part of the data to see if it was a good fit. The model had a best fit
percentage of 83.55\% for the generated voltage data, and a best fit of 39.33\%
for the speed data. The frequency response of the model was estimated with
spectral analysis and bode plots were also created. The tutorial explained that
if the data doesn’t give nice models, then it is best to try out submodels for
the different channels. Two single-input single-output (SISO) models were
created and compared with the existing multiple-input multiple-output (MIMO)
model and the actual data. The Nyquist plots were also compared. Both SISO
models performed well during these comparisons. The next step in the tutorial
was to create a multiple-input single-output (MISO) model in order to get a
model that more accurately reflected the generated voltage data. By creating
this model and comparing it to the validation data and previous models, we saw a
best fit percentage of 90.18\%. The last thing the example showed was how to
merge the two SISO models we created earlier.

@@

\section{System Requirements}
The vehicle plant model will fulfill the requirements listed below:
\begin{itemize}
    \item The resulting plant model will consist of accurate subsystem models, as defined above
    \item The subsystems can be used to create a HIL testbench
    \item The subsystems can handle very small changes in values accurately
\end{itemize}

@@

@@

  \end{tikzpicture}
  % \captionsetup{justification=centering, margin=3cm}
  % \includegraphics[width=2.5in]{figs/inkscape/steeringModelBlockDiagram}
  \caption{Steering subsystem block diagram.}
  \label{fig:steeringModelBlockDiagram}
\end{figure}

@@

 \subsection{Specifications}
 Based on the system requirements listed above, the plant model will meet the following specifications:
 \begin{itemize}
    \item The steering subsystem will be modeled first due to its non-linearities, depicted in Fig.~\ref{fig:nonlinGraph}, and because it is important to the operation of the vehicle 
    \item The steering subsystem will be able to handle small steering angles
    \item Each vehicle subsystem will be modeled separately
 \end{itemize}

@@

\section{Main Project Work (Modeling Vehicle Subsystems)}
To start this project, we first read documentation outlining the uses of MATLAB's System Identification Toolbox. From there we worked on MATLAB tutorials on how to model systems from data using System Identification and then find the most accurate model. We specifically tried to find examples with Multiple-Input Multiple-Output (MIMO) and Multiple-Input Single-Output (MISO) systems, since most of the vehicle subsystems we will model fall into one of these categories. A literature review was also conducted to see how systems with small non-linearities like our steering subsystem were modeled using System Identification. On October 7th we traveled to AutonomouStuff in order to collect data from the steering, acceleration, and braking subsystems in an autonomous vehicle. The data we collected will be used to generate and then verify our models. We collected data on the Lexus RX450H vehicle platform shown in Fig.~\ref{fig:lexusvehicle}. %
%
\begin{figure}[htbp]
	\centering
	\includegraphics[height=4cm]{figs/img/picturesVisitToAStuff/visitors1-20211007}
	\caption{AutonomouStuff Lexus RX450H vehicle.}
	\label{fig:lexusvehicle}
\end{figure}

@@

\section{Validation and Testing} \label{sec:simresults}
\subsection{Steering Subsystem}
In Fig.~\ref{byWireSteerModel}, the output steering angle is plotted versus time
when the vehicle is in by-wire mode. The figure shows the output steering angle
from some data collected to depict the steering system behavior plotted with the
behavior of the estimated model. The best fit percentage for this model is
85.54\%. Likewise, Fig.~\ref{manualSteerModel} depicts the output steering angle
plotted versus time when the vehicle is in manual mode. The best fit percentage
for this model is 90.27\%.

@@

\subsection{Acceleration System}
In \autoref{byWireAccelModel}, the output acceleration pedal position is plotted versus time when the vehicle is in by-wire mode. The figure shows the output acceleration pedal position from some data collected to depict the acceleration system behavior plotted with the behavior of the estimated model. The best fit percentage for this model is 97.69\%. Likewise, \autoref{manualAccelModel} depicts the output acceleration pedal position plotted versus time when the vehicle is in manual mode. The best fit percentage for this model is 98.3\%.

@@

\noindent Table~\ref{tab:manualAccelCoeffB} shows the coefficients of the twenty-fourth order transfer function for the output acceleration pedal position with respect to the input torque voltage B signal.%
%
\begin{table}[hbtp]
	\caption{Manual Mode Acceleration Transfer Function Torque Voltage B Coefficient Table}
	\label{tab:manualAccelCoeffB}
  \centering
  \resizebox{\linewidth}{!}{% Resize table to fit within \linewidth horizontally
    \begin{tabular}{*{25}{c}}
      \toprule
      $a_0$& $a_1$&$a_2$&$a_3$&$a_4$&$a_5$&$a_6$&$a_7$&$a_8$&$a_9$&$a_{10}$&$a_{11}$&$a_{12}$&$a_{13}$&$a_{14}$&$a_{15}$&$a_{16}$&$a_{17}$&$a_{18}$ &$a_{19}$&$a_{20}$&$a_{21}$&$a_{22}$&$a_{23}$&$a_{24}$\\
      \midrule
      5.224E6 & 4.205E7 & 1.429E8 & 3.233E8 & 5.444E8 & 7.326E8 & 8.247E8 & 7.402E8 & 6.301E8 & 3.99E8 & 2.731E8 & 1.264E8 & 7.223E7 & 2.48E7 & 1.216E7 & 3.084E6 & 1.324E6 & 2.422E5 & 9.264E4 & 1.159E4 & 4003 & 307.4 & 96.87 & 3.451 & 1\\
      \bottomrule
    \end{tabular}}
    \begin{center}
    	\resizebox{0.4\linewidth}{!}{% Resize table to fit within \linewidth horizontally
    \begin{tabular}{*{7}{c}}
      \toprule
      $b_0$& $b_1$&$b_2$&$b_3$&$b_4$&$b_5$&$b_6$\\
      \midrule
      -4.159E6 & 1.851E6 & -4.457E6 & 9.043E5 & -7.45E5 & 1.865E5 & -1.545E4\\
      \bottomrule
    \end{tabular}}
    \end{center}	
\end{table}
%
\subsection{Brake System}
The brake system was modeled using only the manual log data. It was trained using the data from the first brake log, and the result and error plots can be seen in \autoref{initalBrakeModel}. The plots show that the model is able to predict the outputs relatively accurately, along with keeping the error below 5\%. In order to further verify the accuracy of the model, it was tested using data from the second brake log. The results from that test, shown in \autoref{testedBrakeModel}, also show that the model can accurately predict the output values and do this within the accepted error bound of 5\%.
\begin{figure}[h]
	\centering
	\subcaptionbox{Model Output Tracking and Error Plots \label{initalBrakeModel}}
		{\includegraphics[width=0.48\linewidth]{figs/img/brake_new_neuralNetworkFig}}
	\subcaptionbox{Model Output Tracking and Error Plots for Log Two Data \label{testedBrakeModel}}
		{\includegraphics[width=0.48\linewidth]{figs/img/brake_new_neuralNetworkFigLog2Test}}
	\caption{Brake System Training Plots}
\end{figure}

@@

>>>>

The example given in~\cite{example1} shows how to create an iddata object from a
dataset in order to get the inputs and the outputs. The next step was to look at
the impulse and step responses in order to learn more about how the inputs and
outputs act. From there the state space model was estimated using the first part
of the given data. This model was compared to the step responses and with the
second part of the data to see if it was a good fit. The model had a best fit
percentage of 83.55\% for the generated voltage data, and a best fit of 39.33\%

for the speed data. The frequency response of the model was estimated with
spectral analysis and bode plots were also created. The tutorial explained that
if the data doesn’t give nice models, then it is best to try out submodels for
the different channels. Two single-input single-output (SISO) models were
created and compared with the existing multiple-input multiple-output (MIMO)
model and the actual data. The Nyquist plots were also compared. Both SISO
models performed well during these comparisons. The next step in the tutorial
was to create a multiple-input single-output (MISO) model in order to get a
model that more accurately reflected the generated voltage data. By creating
this model and comparing it to the validation data and previous models, we saw a
best fit percentage of 90.18\%. The last thing the example showed was how to
merge the two SISO models we created earlier.

@@

@@

% 
\begin{figure}[htbp]
	\centering
	\includegraphics[height=4cm]{figs/img/picturesVisitToAStuff/visitors1-20211007}
	\caption{AutonomouStuff Lexus RX450H vehicle.}
	\label{fig:lexusvehicle}
\end{figure}

@@

  \end{tikzpicture}
  % \captionsetup{justification=centering, margin=3cm}

  % \includegraphics[width=2.5in]{figs/inkscape/steeringModelBlockDiagram}
  \caption{Steering subsystem block diagram.}
  \label{fig:steeringModelBlockDiagram}
\end{figure}

@@

 \section{Modeling Dynamic System using Neural Network}

 In this section, we illustrate how a neural network can be used to model a
 dynamic system in general. Neural network is a system approximation technique
 that .......
 The main structure of a neural network consists neurons, input layer of
 neurons, one or more hidden layers, and the output layer of neurons. The
 neurons of the hidden layers and the output layer have processing capabilities.
 The actual network of a nural network following parallel and distributed system
 architecture. .....

 \missingfigure{Add a generic picture/block diagram of a multiple-input multiple output
   dynamic system}
 \todo[inline]{Add a generic picture of a neural network}
 \todo[inline]{Weights of a neural network}

 \todo[inline]{Training of a neural network}
 \todo[inline]{Testing a neural network}

@@

\subsection{System Requirements}
Based on the system requirements listed above, the plant model will meet the following specifications:
\begin{itemize}
\item The steering subsystem will be modeled first due to its non-linearities, depicted in Fig.~\ref{fig:nonlinGraph}, and because it is important to the operation of the vehicle 
\item The steering subsystem will be able to handle small steering angles
\item Each vehicle subsystem will be modeled separately
\end{itemize}
The vehicle plant model will fulfill the requirements listed below:
\begin{itemize}
    \item The resulting plant model will consist of accurate subsystem models, as defined above
    \item The subsystems can be used to create a HIL testbench
    \item The subsystems can handle very small changes in values accurately
\end{itemize}

\todo[inline]{Add subsections for each subsystem on how NNs are used to model each subsystem}

\todo[inline]{For each subsystem you will need to draw different NN structure }

\section{Validation and Testing} \label{sec:simresults}

To start this project, we first read documentation outlining the uses of
MATLAB's System Identification Toolbox. From there we worked on MATLAB tutorials
on how to model systems from data using System Identification and then find the
most accurate model. We specifically tried to find examples with Multiple-Input
Multiple-Output (MIMO) and Multiple-Input Single-Output (MISO) systems, since
most of the vehicle subsystems we will model fall into one of these categories.
A literature review was also conducted to see how systems with small
non-linearities like our steering subsystem were modeled using System
Identification.

\subsection{Experimental Setup}
\label{sec:experimentalSetup}

On October 7th we traveled to AutonomouStuff in order to collect
data from the steering, acceleration, and braking subsystems in an autonomous
vehicle. The data we collected will be used to generate and then verify our
models. We collected data on the Lexus RX450H vehicle platform shown in
Fig.~\ref{fig:lexusvehicle}. %

@@

\subsection{Transfer Function Modeling}
\label{sec:TransferFunctionModeling}

\todo[inline]{Discuss results using the setup you explained in the previous section. See some IEEE papers}

\subsubsection{Steering Subsystem}
In Fig.~\ref{byWireSteerModel}, the output steering angle is plotted versus time
when the vehicle is in by-wire mode. The figure shows the output steering angle
from some data collected to depict the steering system behavior plotted with the
behavior of the estimated model. The best fit percentage for this model is
85.54\%. Likewise, Fig.~\ref{manualSteerModel} depicts the output steering angle
plotted versus time when the vehicle is in manual mode. The best fit percentage
for this model is 90.27\%.

@@

\subsubsection{Acceleration System}
In \autoref{byWireAccelModel}, the output acceleration pedal position is plotted versus time when the vehicle is in by-wire mode. The figure shows the output acceleration pedal position from some data collected to depict the acceleration system behavior plotted with the behavior of the estimated model. The best fit percentage for this model is 97.69\%. Likewise, \autoref{manualAccelModel} depicts the output acceleration pedal position plotted versus time when the vehicle is in manual mode. The best fit percentage for this model is 98.3\%.

@@

\noindent Table~\ref{tab:manualAccelCoeffB} shows the coefficients of the twenty-fourth order transfer function for the output acceleration pedal position with respect to the input torque voltage B signal.%
%
\begin{table}[hbtp]
	\caption{Manual Mode Acceleration Transfer Function Torque Voltage B Coefficient Table}
	\label{tab:manualAccelCoeffB}
  \centering
  \resizebox{\linewidth}{!}{% Resize table to fit within \linewidth horizontally
    \begin{tabular}{*{25}{c}}
      \toprule
      $a_0$& $a_1$&$a_2$&$a_3$&$a_4$&$a_5$&$a_6$&$a_7$&$a_8$&$a_9$&$a_{10}$&$a_{11}$&$a_{12}$&$a_{13}$&$a_{14}$&$a_{15}$&$a_{16}$&$a_{17}$&$a_{18}$ &$a_{19}$&$a_{20}$&$a_{21}$&$a_{22}$&$a_{23}$&$a_{24}$\\
      \midrule
      5.224E6 & 4.205E7 & 1.429E8 & 3.233E8 & 5.444E8 & 7.326E8 & 8.247E8 & 7.402E8 & 6.301E8 & 3.99E8 & 2.731E8 & 1.264E8 & 7.223E7 & 2.48E7 & 1.216E7 & 3.084E6 & 1.324E6 & 2.422E5 & 9.264E4 & 1.159E4 & 4003 & 307.4 & 96.87 & 3.451 & 1\\
      \bottomrule
    \end{tabular}}
    \begin{center}
    	\resizebox{0.4\linewidth}{!}{% Resize table to fit within \linewidth horizontally
    \begin{tabular}{*{7}{c}}
      \toprule
      $b_0$& $b_1$&$b_2$&$b_3$&$b_4$&$b_5$&$b_6$\\
      \midrule
      -4.159E6 & 1.851E6 & -4.457E6 & 9.043E5 & -7.45E5 & 1.865E5 & -1.545E4\\
      \bottomrule
    \end{tabular}}
    \end{center}	
\end{table}
%
\subsubsection{Brake System}
The brake system was modeled using only the manual log data. It was trained using the data from the first brake log, and the result and error plots can be seen in \autoref{initalBrakeModel}. The plots show that the model is able to predict the outputs relatively accurately, along with keeping the error below 5\%. In order to further verify the accuracy of the model, it was tested using data from the second brake log. The results from that test, shown in \autoref{testedBrakeModel}, also show that the model can accurately predict the output values and do this within the accepted error bound of 5\%.
\begin{figure}[h]
	\centering
	\subcaptionbox{Model Output Tracking and Error Plots \label{initalBrakeModel}}
		{\includegraphics[width=0.48\linewidth]{figs/img/brake_new_neuralNetworkFig}}
	\subcaptionbox{Model Output Tracking and Error Plots for Log Two Data \label{testedBrakeModel}}
		{\includegraphics[width=0.48\linewidth]{figs/img/brake_new_neuralNetworkFigLog2Test}}
	\caption{Brake System Training Plots}
\end{figure}

@@

\subsection{Neural Network Modeling}
\label{sec:NN-Modeling}

\todo[inline]{Discuss results  NN modeling using the setup you explained in the previous section. See some IEEE papers}

\subsection{Discussion}
\label{sec:discussion}

\todo[inline]{Discuss pros and cons of the results you presented in the previous sections on each of the techniques you incorporated}

\section{Conclusion and Future Work}
\label{sec:conclustionAndFutureWork}

\todo[inline]{One paragraph on conclusion, make sure you to recommend what modeling technique for the company }
\todo[inline]{One paragraph on future work}
